Another paper with lots of text and fancy pictures

### 2023-11-09 paper.tex
Replace pictures

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/aniso.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
    the axis $Y$. Anisotropicity of the medium can be seen on a heatmap of $S_3$
    function (in the middle). An average of 10 $S_3$ evaluations of the medium
    rotated by a random angle is on the right.}
  \label{fig:aniso}
\end{figure}

>>>>

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/aniso.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
    the vector $(1, 1)$. Anisotropicity of the medium can be seen on a heatmap
    of $S_3$ function (in the middle). An average of 120 $S_3$ evaluations of
    the medium rotated by a random angle is on the right.}
  \label{fig:aniso}
\end{figure}
